Resilience and Home-Space for WSTS \thanks{This work was partly done while the authors were supported by the Agence Nationale de la Recherche grant BraVAS (ANR-17-CE40-0028).}

### 2023-10-28 VMCAI-revised-version/final.tex
effectivity

On the positive side, let us recall a result about {\sc Bounded-state-resilience} (called resilience in \cite{DBLP:conf/gg/Ozkan22,DBLP:journals/corr/abs-2108-00889}).
%
%		(\"Ozkan,   \"Ozkan and W{\"{u}}rdemann,  
%
\begin{theorem}[Theorem 1,~\cite{DBLP:conf/gg/Ozkan22}, Theorem 1, ~\cite{DBLP:journals/corr/abs-2108-00889}]\label{ref ozkan}
{\sc Bounded-state-resilience} and {\sc $k$-state-resilience} are decidable for $\pred$-basis-effective, $\post^*$-basis-effective WSTS with strong compatibility
when
$\Safe=\mathop{\uparrow} \Safe$.
\end{theorem}

We may immediately  \emph{generalize} this last result by strengthening to \emph{unbounded} {\sc State-resilience}. The proof is essentially the same than the previous one.

\begin{proposition}\label{postcomputable}
{\sc State-resilience} is decidable for $\pred$-basis-effective, $\post^*$-basis-effective WSTS with strong compatibility
when
$\Safe=\mathop{\uparrow} \Safe$.
\end{proposition}

\begin{proof}
\alain{où utilise-t-on la strong compatibility ? et si on ne l'utilise pas, c'est le theo 8...}
Since $\mathscr{S}$ is a WSTS there exists an $n_0 \in \N$ such that
$\pred^*(\Safe) =  \pred^{\leq n_0}(\Safe)$. We can compute the least $n_0$ by iteratively computing 
$\pred^{\leq n+1}(\Safe)$ from $\pred^{\leq n}(\Safe)$, checking 
$\pred^{\leq n+1}(\Safe) = \pred^{\leq n}(\Safe)$, 
returning $n$ if that is the case.
Then, because {\sc $n_0$-state-resilience} is decidable, 
checking $\mathop{\uparrow} \post^*(s) 
 \subseteq \pred^{\leq n}(\Safe) = \pred^*(\Safe)$ is,
and {\sc State-resilience} is decidable. \qed
\end{proof}

The proof of Theorem~\ref{ref ozkan} rely on the computability of $\mathop{\uparrow} \post^*(s)$ and on the following lemma.

@@

\alain{plus fort que prop 6}
\begin{theorem}\label{post srp}
{\sc State-resilience} is decidable for $\pred$-basis-effective, $\post^*$-basis-effective WSTS
when
$\Safe=\mathop{\uparrow} \Safe$. 
\end{theorem}

\begin{proof}
Let $\mathscr{S}$ be a $\pred$-basis-effective, $\post^*$-basis-effective WSTS.
%
Since $\mathscr{S}$ is $\post^*$-basis-effective, let $B_{\mathop{\uparrow} \post^*(s)}$ 
 be a finite basis of $\mathop{\uparrow} \post^*(s)$, hence $\mathop{\uparrow} \post^*(s) = \mathop{\uparrow} B_{\mathop{\uparrow} \post^*(s)}$.
%
Let $B_\Safe$ be a finite basis of $\Safe$, hence $\Safe = .\mathop{\uparrow} B_\Safe$.
%
Since $\mathscr{S}$ is $\pred$-basis-effective, we may compute a finite basis $B_{\pred^*(\Safe)}$ of $\pred^*(\Safe)$ from $B_\Safe$.
%
\alain{je pense qu'il y a une erreur, on n'utilise pas le Lemme 2}
%
By applying Lemma~\ref{Lemma intersection} twice,
we obtain that 
\[ \post^*(s) 
 \subseteq \pred^*(\Safe) \text{ iff } B_{\mathop{\uparrow} \post^*(s)}  
 \subseteq \pred^*(\Safe)\]
%
%
\alain{je pense qu'il y a une erreur, je propose plutôt}
%
Recall that $\mathscr{S}$ is state-resilient iff  $\post^*(s) 
 \subseteq \pred^*(\Safe)$ iff 
\[ \mathop{\uparrow} B_{\mathop{\uparrow} \post^*(s)} 
 \subseteq \mathop{\uparrow}  B_{\pred^*(\Safe)} \text{ iff } \forall b \in B_{\mathop{\uparrow} \post^*(s)}  \exists b' \in B_{\pred^*(\Safe)} \text{ such that } b' \leq b \]
%
Since both $B_{\mathop{\uparrow} \post^*(s)}$ and $B_{\pred^*(\Safe)}$ are finite, {\sc State-resilience} is decidable.
%
\alain{ce qui suit est à enlever je l'ai commenté (à vérifier)}
%
%			Since $B_{\mathop{\uparrow} \post^*(s)}$ is finite
%\alain{comment calcule-t-on une telle base sans l'hypothèse $\pred$-basis-effective qui n'est pas dans les hypothèses du théorème ? Est-elle chez Ozkan ?} 
%			we can check that $B_{\mathop{\uparrow} \post^*(s)} 
%			 \setminus \pred^*(\Safe) = \emptyset$.  \qed
\end{proof}

>>>>

On the positive side, let us recall a result about {\sc Bounded-state-resilience} (called resilience in \cite{DBLP:conf/gg/Ozkan22,DBLP:journals/corr/abs-2108-00889}).
%
%		(\"Ozkan,   \"Ozkan and W{\"{u}}rdemann,  
%
\begin{theorem}[Theorem 1,~\cite{DBLP:conf/gg/Ozkan22}, Theorem 1, ~\cite{DBLP:journals/corr/abs-2108-00889}]\label{ref ozkan}
{\sc Bounded-state-resilience} and {\sc $k$-state-resilience} are decidable for $\pred$-basis-effective, $\post^*$-basis-effective WSTS with strong compatibility
when
$\Safe=\mathop{\uparrow} \Safe$.
\end{theorem}
%
%
%\alain{ce qui suit est à supprimer car subsumé par Theo 8}
%%
%We may immediately  \emph{generalize} this last result by strengthening to \emph{unbounded} {\sc State-resilience}. The proof is essentially the same than the previous one.
%
%\begin{proposition}\label{postcomputable}
%{\sc State-resilience} is decidable for $\pred$-basis-effective, $\post^*$-basis-effective WSTS with strong compatibility
%when
%$\Safe=\mathop{\uparrow} \Safe$.
%\end{proposition}
%
%\begin{proof}
%\alain{où utilise-t-on la strong compatibility ? et si on ne l'utilise pas, c'est le theo 8...}
%Since $\mathscr{S}$ is a WSTS there exists an $n_0 \in \N$ such that
%$\pred^*(\Safe) =  \pred^{\leq n_0}(\Safe)$. We can compute the least $n_0$ by iteratively computing 
%$\pred^{\leq n+1}(\Safe)$ from $\pred^{\leq n}(\Safe)$, checking 
%$\pred^{\leq n+1}(\Safe) = \pred^{\leq n}(\Safe)$, 
%returning $n$ if that is the case.
%Then, because {\sc $n_0$-state-resilience} is decidable, 
%checking $\mathop{\uparrow} \post^*(s) 
% \subseteq \pred^{\leq n}(\Safe) = \pred^*(\Safe)$ is,
%and {\sc State-resilience} is decidable. \qed
%\end{proof}
%%
%\alain{ce qui précède est à supprimer car subsumé par Theo 8}
%
The proof of Theorem~\ref{ref ozkan} rely on the computability of $\mathop{\uparrow} \post^*(s)$ and on the following lemma.

@@

%\alain{Theo 8 est plus fort que prop 6}
\begin{theorem}\label{post srp}
{\sc State-resilience} is decidable for $\pred$-basis-effective, $\post^*$-basis-effective WSTS
when
$\Safe=\mathop{\uparrow} \Safe$. 
\end{theorem}

\begin{proof}
Let $\mathscr{S}$ be a $\pred$-basis-effective, $\post^*$-basis-effective WSTS.
%
Since $\mathscr{S}$ is $\post^*$-basis-effective, let $B_{\mathop{\uparrow} \post^*(s)}$ 
 be a finite basis of $\mathop{\uparrow} \post^*(s)$, hence $\mathop{\uparrow} \post^*(s) = \mathop{\uparrow} B_{\mathop{\uparrow} \post^*(s)}$.
%
Let $B_\Safe$ be a finite basis of $\Safe$, hence $\Safe = .\mathop{\uparrow} B_\Safe$.
%
Since $\mathscr{S}$ is $\pred$-basis-effective, we may compute a finite basis $B_{\pred^*(\Safe)}$ of $\pred^*(\Safe)$ from $B_\Safe$.
%
%
By applying Lemma~\ref{Lemma intersection} twice,
we obtain that 
\[ \post^*(s) 
 \subseteq \pred^*(\Safe) \text{ iff } \mathop{\uparrow} \post^*(s)
 \subseteq \pred^*(\Safe)\]
%
%
%
%Recall that $\mathscr{S}$ is state-resilient iff  $\post^*(s) 
% \subseteq \pred^*(\Safe)$ iff 
Now the last inclusion is equivalent to:
\[ \mathop{\uparrow} B_{\mathop{\uparrow} \post^*(s)} 
 \subseteq \mathop{\uparrow}  B_{\pred^*(\Safe)} \text{ iff } \forall b \in B_{\mathop{\uparrow} \post^*(s)}  \exists b' \in B_{\pred^*(\Safe)} \text{ such that } b' \leq b \]
%
Since both $B_{\mathop{\uparrow} \post^*(s)}$ and $B_{\pred^*(\Safe)}$ are finite, {\sc State-resilience} is decidable.\qed
%
%
%			Since $B_{\mathop{\uparrow} \post^*(s)}$ is finite
%\alain{comment calcule-t-on une telle base sans l'hypothèse $\pred$-basis-effective qui n'est pas dans les hypothèses du théorème ? Est-elle chez Ozkan ?} 
%			we can check that $B_{\mathop{\uparrow} \post^*(s)} 
%			 \setminus \pred^*(\Safe) = \emptyset$.  \qed
\end{proof}
